---
title: "Fuel Efficieny"
author: "Doug Ashton"
date: "20 April 2016"
output: html_document
---

### Data Sources

I'm adding data to a Google Docs spreadsheet everytime I refuel.

```{r}
df <- read.csv("PetrolFocus.csv")
```

### Cleaning

Some rows are missing the number of miles and so are being removed.

```{r}
df$Date <- as.Date(df$Date, format="%d/%m/%Y")
df$Index <- 1:nrow(df)

# Clean missing miles
df <- df[!is.na(df$Miles), ]

# Clean silly numbers
df <- df[df$Miles.Gallon < 50, ]
```

### Impute missing date values

Some dates are missing. Rather than lose the data we will make a linear interpolation to choose an approximate date.

```{r}
dfx <- data.frame(Index=df$Index, Date=as.numeric(df$Date))
fit <- lm(Date ~ Index, data=dfx)

x <- is.na(df$Date)
df$Date[x] <- as.Date(round(predict(fit, df[x, "Index", drop=FALSE])), origin="1970-01-01")
```

### Time series

```{r, message=FALSE, warning=FALSE}
library(zoo)
mpg <- zoo(df$Miles.Gallon, order.by = df$Date)

df$Year <- lubridate::year(df$Date)

plot(mpg)
```

### Year on year

```{r}
library(ggplot2)

qplot(y=Miles.Gallon, x=as.factor(Year), data=df, geom="boxplot")

```

So is 2016 worse than 2015?

```{r}
t.test(df$Miles.Gallon[df$Year==2015], 
       df$Miles.Gallon[df$Year==2016])
```

Can you think of a whole bunch of issues with this test?
